\section{Bibliography}

\begin{thebibliography}{9}

\bibitem{bennet1996}
    Stuart Bennet,
    \emph{A Brief History of Automatic Control},
    IEEE Control Systems Magazine,
    volume 16,
    issue 3,
    June 1996,
    pages 17-25,
    doi: 10.1109/37.506394.

\bibitem{cassel1914}
    Gustav Cassel,
    \emph{Money and Foreign Exchange After 1914},
    Macmillan,
    1923,
    p.137.

\bibitem{feller1957}
    William Feller,
    \emph{An Introduction to Probability Theory and its Applications}
    John Wiley and Sons,
    1957.

\bibitem{fisher1926}
    Irving Fisher, 
        \emph{A Statistical Relation between Unemployment and Price Changes}
        International Labour Review,
        1926,
        volume 13,
        pages 496-502,
        1926.

\bibitem{fisher1896}
    Irving Fisher,
        \emph{Appreciation and Interest}
        1896.

\bibitem{hamming1950}
    R.W.Hamming,
        \emph{Error Detecting and Error Correcting Codes},
        The Bell System Technical Journal,
        volume 14,
        number 2,
        April 1950,
        pages 147-160.

\bibitem{hughes1971}
    T.P.Hughes,
        \emph{Elmer Sperry: Inventor and Engineer}
        1971.

\bibitem{hume1741}
    David Hume,
        \emph{Of Money, Essays, Moral, Political and Literary},
        1741.

\bibitem{lucas1996}
    Robert E. Lucas Jr.,
        \emph{Nobel Lecture: Money Neutrality},
        The Journal of Political Economy,
        1996,
        volumet 104,
        pages 661-682.

\bibitem{mackay2003}
    David J.S. MacKay,
        \emph{Information Theory, Inference, and Learning Algorithms},
        Cambridge University Press,
        2003.

\bibitem{phillips1958}
    A.W. Phillips,
        \emph{The Relation between Unemployment and the Rate of Change of Money Wage Rates in the United Kingdom, 1861-1957},
        Economica,
        1958,
        volume 25,
        pages 283-299.

\bibitem{shannon1945}
    Claude E. Shannon,
    \emph{Communication Theory of Secrecy Systems},
    1945,
    pages 84-143.

\bibitem{shannon1948}
    Claude E. Shannon,
    \emph{A Mathematical Theory of Communication},
    The Bell System Technical Journal,
    volume 27,
    pages 379-412,
    1948.

\bibitem{shiller1998}
    Robert J Shiller,
    \emph{Indexed Units of Account: Theory and Assessment of Historical Experience},
    NBER Working Paper Series,
    volume 6356,
    1998.

\bibitem{abildren2011}
    Kim Abildren and Jens Thomsen,
    \emph{A Tale of Two Danish Banking Crisis},
    Monetary Review,
    Danmarks Nationalbank,
    1st Quarter 2011,
    volume 1,

\bibitem{astrom2009}
    Karl Johan Astrom and Richard M. Murray,
    \emph{Feedback Systems: An Introduction for Scientists and Engineers},
    2009.

\bibitem{douglas2019}
    Brian Douglas,
    \emph{The Fundamentals of Control Theory},
    2019.

\bibitem{douglas1939}
    Paul H. Douglas et al,
    \emph{A Program for Monetary Reform},
    1939.

\bibitem{einaudi2006}
    Luigi Einaudi,
    \emph{The Theory of Imaginary Money from Charlemagne to the French Revolution},
    2006.

\bibitem{honkapohja2009}
    Seppo Honkapohja,
    \emph{The 1990's Financial Crises in Nordic Countries},
    Bank of Finland Research Discussion Papers,
    2009,
    volume 5.

\bibitem{jevons1876}
    William Stanley Jevons,
    \emph{Money and the Mechanism of Exchange},
    1876,
    chapter 25.

\bibitem{keynes1914}
    John Maynard Keynes,
    \emph{A Treatise on Money},
    1914,
    volume 1,
    chapter 1,
    Money and Money-of-Account.

\bibitem{keynes1936}
    John Maynard Keynes,
    \emph{The General Theory of Employment, Interest, and Money},
    1936.

\bibitem{lefort:2002}
    Fernando Lefort and Klaus Schmedt-Hebbel,
    \emph{Indexation, Inflation and Monetary Policy: An Overview},
    Central Bank of Chile,
    2002.

\bibitem{marshall1925}
    A.C. Pigou,
    \emph{Remedies for Fluctuations in General Prices},
    in Memorials of Alfred Marshall,
    1925.

\bibitem{maxwell1868}
    J. Clerk Maxwell,
    \emph{On Governors},
    March 5, 1968.

\bibitem{mill1848}
    John Stuart Mill,
    \emph{Principles of Political Economy},
    1848.

\bibitem{minorsky1922}
    Nicolas Minorsky,
    \emph{Directional Stability of Automatically Steered Bodies},
    Naval Engineers Journal,
    volume 32,
    issue number 2,
    1922.

\bibitem{mogul2005}
    Jeffrey C. Mogul,
    \emph{Emergent (Mis)behavior vs. Complex Software Systems},
    HP Laboratories,
    2005.

\bibitem{sperry1913}
    Elmer A. Sperry,
    \emph{Engineering Applications of the Gyroscope},
    Journal of the Franklin Institute,
    volume 175,
    Number 5,
    May 1913.

\bibitem{wescott2016}
    Tim Wescott,
    \emph{PID Without a PhD},
    2016.

\bibitem{wright1908}
    Orville and Wilbur Wright,
    \emph{The Wright Brothers Aeroplane},
    Century Magazine,
    September 1908.

\end{thebibliography}

